ML Estimation of Matrix--$t$ Distributions with Expectation Maximization

### 2017-01-14 paper.tex
Working on the subsection for EM.

\documentclass[english,listof=totoc]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage[authoryear]{natbib}
\usepackage[unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
 breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
 {hyperref}\usepackage{mathtools}

@@

\section{EM formulae for matrix--$t$ distribution}\label{sec:derivation}

@@

\subsection{Calculating the Expectation-maximization steps}

>>>>

\documentclass[english,listof=totoc]{scrartcl}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amsthm}
\usepackage[authoryear]{natbib}
\usepackage[unicode=true,pdfusetitle,
 bookmarks=true,bookmarksnumbered=false,bookmarksopen=false,
 breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
 {hyperref}\usepackage{mathtools}

@@

\section{EM for matrix--$t$ distribution}\label{sec:derivation}

@@

\subsection{EM formulas for matrix--$t$ distribution}

Given a random variable $X$ with probability distribution with density (or mass) function $p_{\theta}(\cdot)$ with $\theta$ dependence. Assume the density (or mass) function is a marginalization over some unobserved random state $Z$, i.e., $p_{\theta}(x)=\mathbb{E}_{\theta}\left[p_{\theta}(x|Z)\right]$. With observations $\left\{x_i\right\}_{i\in I}$ the classical EM method of MLE consists of two step:

\begin{itemize}
\item At the $n$-th iteration, compute the conditional expectations with respect to $Z$
\begin{equation}
Q(\theta|\theta_n):=\sum_{i\in I}\mathbb{E}_{\theta_n}\left[\log p_{\theta}(x_i,Z)|x_i\right].
\end{equation}

\item Update $\theta$ by maximizing $Q(\theta|\theta_n)$, i.e., $\theta_{n+1} = \textrm{argmax}_{\theta}\,Q(\theta|\theta_n)$.
\end{itemize}

For matrix--$t$ distributions,
